The History of Social Work Research: A Data Science Perspective

### 2015-02-03 Analysis.Rmd
Minor changes.

#add no authorship indicated
#Anonymous
x.temp <- filter(bwr.df, attributes == "article")
x.temp2 <- filter(bwr.df, attributes == "journal")

>>>>

#add no authorship indicated
#Anonymous
x.temp <- filter(bwr.df, attributes == "article")
x.temp2 <- filter(bwr.df, attributes == "journal")
x.temp3 <- filter(bwr.df, attributes == "abstract")

dim(x.temp); dim(x.temp2); dim(x.temp3)

dim(x.temp)

lapply(checks, dim)
